---
title: "Leaflet Quito map"
author: "Carlos Andres Pillajo"
date: "11/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Developing data products

##  Instructions:

Create a web page using R Markdown that features a map created with Leaflet. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. 

## Submission

The next map shows and example of a map from my city Quito, Ecuador. Markers represent the principal urban parks from the city.

```{r warning=FALSE}
library(leaflet)
my_map <- leaflet() %>%
  addTiles() %>%
addMarkers(lat=-0.16145497082457894, lng=-78.47787996303607)
parksLatLong <- data.frame(
lat = c(-0.182834, -0.140591, -0.18011468816008858),
lng = c(-78.484319, -78.48831195120508, -78.46698742150272),
popup = c("La Carolina", "Bicentenario", "Metropolitano"))
parksLatLong %>%
leaflet() %>%
addTiles() %>%
addMarkers()

```
